% 
\section{Introduction}
\label{results:introduction}
% 
The results section presents the findings obtained from the research methods. It offers a clear, organized presentation of raw data, often utilizing tables, figures, or graphs to enhance understanding. The section focuses on facts and avoids interpretation or analysis, letting the data speak for itself. Rules for this section demand precision and objectivity. Results must be reported accurately, and any trends or patterns should be highlighted without bias. Every piece of data presented should directly relate to the research questions, ensuring relevance. Clarity is paramount; the information should be presented logically, guiding readers through the findings in a comprehensible manner, setting the stage for the subsequent analysis and discussion.


% 
\section{Evaluation and Discussion}
\label{results:evaluation}
% 
The evaluation and discussion section interprets the results within the context of the research questions and existing literature. It critically analyzes the findings, explores their implications, and assesses their significance. This section evaluates the study's strengths and limitations, addressing unexpected results and explaining their possible causes. Rules for this section demand depth and insight. It must demonstrate a clear understanding of the research's implications, relating the findings to the broader field of study. Critical thinking is essential; the discussion should offer reasoned interpretations, considering alternative explanations.
